### 2018-06-12 express2018/unique.tex
I have to use labels without hypen and underscore (don't know why) to prevent strange LaTeX compilation errors.

\begin{definition}
\label{d:uni_contra}
Given a  system of contractions 
$\{  X_i \mcontr E_i\}_{i\in I}$, 
 we say that:
\begin{itemize}
\item
 $\til P$ is a \emph{solution  for $\mcontrBIS$ of the 
 system of contractions} 
 if $\til P \mcontrBIS \til E [\til P]$;
\item 
the system  
has  \emph{a unique 
solution for $\asymp$}
if 
whenever 
 $\til P$ and $\til Q$ are both solutions  for  $\mcontrBIS$
 then $\til P \asymp \til Q$.
\qed\end{itemize}
\end{definition}

@@

\begin{theorem}[unique solution of contractions for $\wb$]
\label{t:contra_bisimulation_u}
A system of weakly-guarded contractions
    has 
a unique solution 
 for $\wb$.
\end{theorem}

@@

\begin{theorem}
\label{t:rcontr-precongruence}
Relation $\rcontr$ is a precongruence in CCS. 
\end{theorem}

>>>>

\begin{definition}
\label{d:uniContra}
Given a  system of contractions 
$\{  X_i \mcontr E_i\}_{i\in I}$, 
 we say that:
\begin{itemize}
\item
 $\til P$ is a \emph{solution  for $\mcontrBIS$ of the 
 system of contractions} 
 if $\til P \mcontrBIS \til E [\til P]$;
\item 
the system  
has  \emph{a unique 
solution for $\asymp$}
if 
whenever 
 $\til P$ and $\til Q$ are both solutions  for  $\mcontrBIS$
 then $\til P \asymp \til Q$.
\qed\end{itemize}
\end{definition}

@@

\begin{theorem}[unique solution of contractions for $\wb$]
\label{t:contraBisimulationU}
A system of weakly-guarded contractions
    has 
a unique solution 
 for $\wb$.
\end{theorem}

@@

\begin{theorem}
\label{t:rcontrPrecongruence}
Relation $\rcontr$ is a precongruence in CCS. 
\end{theorem}
